---
title: "Data_Processing_Optimal_Parm"
author: "Vinuraj Devaraj"
date: "4/29/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lsr)
# Read data set
data_df = read.csv("D:/PhD Program/Final Research/Dissertation/Writeup/best_parm_data.csv")
```

## R Markdown
 Read dataset and convert the variables to factors, especially those whose impact needs to be assessed


```{r cars}
# Convert variables to determine impact to factors
data_df$Anomaly.Treated. <- as.factor(data_df$Anomaly.Treated)
data_df$Hilbert.Transformed. <- as.factor(data_df$Hilbert.Transformed.)
data_df$MFCC.included. <- as.factor(data_df$MFCC.included.)
data_df$Sample.Duration <- as.factor(data_df$Sample.Duration)
data_df$Data.Scaled. <- as.factor(data_df$Data.Scaled.)

```

## Perform Kruskal Wallis test
Perform Kruskal Wallis test to determine significance of data augmentation 

```{r data_aug, echo=FALSE}
kruskal_model <- kruskal.test(Best.Accuracy~Sample.Duration, data=data_df)
print(kruskal_model)
print("Effect Size")
lsr::cohensD(data_df$Best.Accuracy~data_df$Sample.Duration)
```


Perform Kruskal Wallis test to determine significance outlier treatement

```{r outlier, echo=FALSE}
kruskal_model <- kruskal.test(Best.Accuracy~Anomaly.Treated., data=data_df)
print(kruskal_model)
print("Effect Size")
lsr::cohensD(data_df$Best.Accuracy~data_df$Anomaly.Treated.)
```
Perform Kruskal Wallis test to determine significance MFCC features

```{r MFCC, echo=False}
kruskal_model <- kruskal.test(Best.Accuracy~MFCC.included., data=data_df)
print(kruskal_model)
print("Effect Size")
lsr::cohensD(data_df$Best.Accuracy~data_df$MFCC.included.)
```
Perform Kruskal Wallis test to determine significance of Hilbert Transformation

```{r hilbert_transform, echo=False}
kruskal_model <- kruskal.test(Best.Accuracy~Hilbert.Transformed., data=data_df)
print(kruskal_model)
print("Effect Size")
lsr::cohensD(data_df$Best.Accuracy~data_df$Hilbert.Transformed.)
```

Perform Kruskal Wallis test to determine significance of data scaling

```{r hilbert_transform, echo=False}
kruskal_model <- kruskal.test(Best.Accuracy~Data.Scaled., data=data_df)
print(kruskal_model)
print("Effect Size")
lsr::cohensD(data_df$Best.Accuracy~data_df$Data.Scaled.)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent 
printing of the R code that generated the plot.
